Project 1 Checkpoint

### 2015-02-27 project1/checkpoint/main.tex
Adding a conclusion and summary

\section{Conclusion}

>>>>

\section{Conclusion}
In summary, I've built a web-based simulation of the 12th and Peachtree intersection in both the North and South
directions. The NGSIM dataset was used for gathering estimations about input rates, and various general statistics about
the cars on Peachtree. Some simplifications were made in order to accomodate lack of data, domain knowledge, and time
(among other things). Furthermore, some of the design choices have their sets of caveats which were noted when building
the simulation. However, the simulation is real-time and does yield relatively intuitive results.
